Fourmile Calibrations and Output

### 2023-05-03 38HRU_model/fourmile_model_outputs.Rmd
added in burn params

library(tidyverse)
library(plotly)
library(lubridate)
library(knitr)
library(kableExtra)
library(dataRetrieval)
library(hydroGOF)
library(sp)
library(raster)
library(sf)
library(mapview)
library(here)
library(scales)
library(dataRetrieval)
library(tmap)
library(ggpubr)
library(gridExtra)

@@

## Burn params

@@

burn_params <- bind_rows(grid_burn, statn_burn) %>%
  ungroup() %>%
  mutate(across(c(luca_a_rain:luca_soilDistMPSLPS), as.numeric)) %>%
  group_by(cal) %>%
  summarise(across(c(luca_a_rain:luca_soilDistMPSLPS), mean)) %>%
  pivot_longer(!cal, 
               names_to = 'params',
               values_to = 'value')

@@

# plot_burnparams <- function(param_name) {
#   params %>%
#     filter(params == param_name) %>%
#     ggplot(aes(x = value,
#                y = cal)) + 
#     geom_point() +
#     ggtitle(param_name) +
#     theme_bw()
# }
# 
# name <- levels(burn_params$params)
# 
# lapply(name, plot_burnparams)

@@

<!-- # Outlet results -->

<!-- ## Hydrograph -->

<!-- ```{r hydrographs, echo = F} -->
<!-- flow <- read_csv('discharge_all.csv') %>% -->
<!--   replace(.==-9999, NA) -->

<!-- flow_pivot <- flow %>% -->
<!--   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>% -->
<!--   mutate(year = as.factor(year(date))) -->

<!-- q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) + -->
<!--   geom_line() + -->
<!--   scale_color_manual(name="cal_run", values=c('obs' = 'black', -->
<!--                                             "grid_2011"="seagreen", -->
<!--                                             "grid_2012"="seagreen2", -->
<!--                                             "grid_2013"="steelblue", -->
<!--                                             "grid_2014"='dodgerblue', -->
<!--                                             "grid_2015" = "cyan3", -->
<!--                                             'grid_2016' = 'blue', -->
<!--                                             'grid_2017' = 'blue4', -->
<!--                                             'grid_2018' = 'cadetblue', -->
<!--                                             'grid_2019' = 'lightgreen', -->
<!--                                             'grid_2020' = 'olivedrab', -->
<!--                                             'grid_all' = 'steelblue3', -->
<!--                                             "statn_2011"="maroon", -->
<!--                                             "statn_2012"="deeppink4", -->
<!--                                             "statn_2013"="deeppink", -->
<!--                                             "statn_2014"='purple', -->
<!--                                             "statn_2015" = "mediumorchid1", -->
<!--                                             'statn_2016' = 'indianred', -->
<!--                                             'statn_2017' = 'sienna', -->
<!--                                             'statn_2018' = 'salmon2', -->
<!--                                             'statn_2019' = 'mediumpurple1', -->
<!--                                             'statn_2020' = 'violetred', -->
<!--                                             'statn_all' = 'red')) -->

<!-- ggplotly(q) -->

<!-- ``` -->

<!-- ## Annual hydrographs -->

<!-- ```{r cy hydrographs, echo = F} -->

<!-- plotq_cy <- function(calyear) { -->
<!--   {flow_pivot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = date, -->
<!--                y = q_m3s, -->
<!--                color = cal_run)) + -->
<!--     geom_line() + -->
<!--         scale_color_manual(name="cal_run", values=c('obs' = 'black', -->
<!--                                             "grid_2011"="seagreen",  -->
<!--                                             "grid_2012"="seagreen2",  -->
<!--                                             "grid_2013"="steelblue", -->
<!--                                             "grid_2014"='dodgerblue',  -->
<!--                                             "grid_2015" = "cyan3", -->
<!--                                             'grid_2016' = 'blue', -->
<!--                                             'grid_2017' = 'blue4', -->
<!--                                             'grid_2018' = 'cadetblue', -->
<!--                                             'grid_2019' = 'lightgreen', -->
<!--                                             'grid_2020' = 'olivedrab', -->
<!--                                             'grid_all' = 'steelblue3', -->
<!--                                             "statn_2011"="maroon",  -->
<!--                                             "statn_2012"="deeppink4",  -->
<!--                                             "statn_2013"="deeppink", -->
<!--                                             "statn_2014"='purple',  -->
<!--                                             "statn_2015" = "mediumorchid1", -->
<!--                                             'statn_2016' = 'indianred', -->
<!--                                             'statn_2017' = 'sienna', -->
<!--                                             'statn_2018' = 'salmon2', -->
<!--                                             'statn_2019' = 'mediumpurple1', -->
<!--                                             'statn_2020' = 'violetred', -->
<!--                                             'statn_all' = 'red')) + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw()} %>% -->
<!--     ggplotly() -->

<!-- } -->

<!-- name <- levels(flow_pivot$year) -->

<!-- try <- lapply(name, plotq_cy) -->

<!-- htmltools::tagList(try) -->

<!-- try -->
<!-- ``` -->

<!-- ## KGE -->

<!-- ### Overall KGE -->

<!-- ```{r kge overall, echo = F} -->

<!-- flow_kge_all <- flow %>% -->
<!--   summarize(grid2011 = KGE(grid_2011, obs), -->
<!--             grid2012 = KGE(grid_2012, obs), -->
<!--             grid2013 = KGE(grid_2013, obs), -->
<!--             grid2014 = KGE(grid_2014, obs), -->
<!--             grid2015 = KGE(grid_2015, obs), -->
<!--             grid2016 = KGE(grid_2016, obs), -->
<!--             grid2017 = KGE(grid_2017, obs), -->
<!--             grid2018 = KGE(grid_2018, obs), -->
<!--             grid2019 = KGE(grid_2019, obs), -->
<!--             grid2020 = KGE(grid_2020, obs), -->
<!--             gridall = KGE(grid_all, obs), -->
<!--             statn2011 = KGE(statn_2011, obs), -->
<!--             statn2012 = KGE(statn_2012, obs), -->
<!--             statn2013 = KGE(statn_2013, obs), -->
<!--             statn2014 = KGE(statn_2014, obs), -->
<!--             statn2015 = KGE(statn_2015, obs), -->
<!--             statn2016 = KGE(statn_2016, obs), -->
<!--             statn2017 = KGE(statn_2017, obs), -->
<!--             statn2018 = KGE(statn_2018, obs), -->
<!--             statn2019 = KGE(statn_2019, obs), -->
<!--             statn2020 = KGE(statn_2020, obs), -->
<!--             statnall = KGE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 2) -->

<!-- flow_kge_all <- flow_kge_all %>% -->
<!--   pivot_longer(everything()) %>% -->
<!--   arrange(value) -->

<!-- kable(flow_kge_all) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- ``` -->

<!-- ### KGE by year -->

<!-- ```{r kge by year, echo = F} -->

<!-- flow_year <- flow %>% -->
<!--   mutate(year = year(date)) %>% -->
<!--   group_by(year) %>% -->
<!--   summarize(grid2011 = KGE(grid_2011, obs), -->
<!--             grid2012 = KGE(grid_2012, obs), -->
<!--             grid2013 = KGE(grid_2013, obs), -->
<!--             grid2014 = KGE(grid_2014, obs), -->
<!--             grid2015 = KGE(grid_2015, obs), -->
<!--             grid2016 = KGE(grid_2016, obs), -->
<!--             grid2017 = KGE(grid_2017, obs), -->
<!--             grid2018 = KGE(grid_2018, obs), -->
<!--             grid2019 = KGE(grid_2019, obs), -->
<!--             grid2020 = KGE(grid_2020, obs), -->
<!--             gridall = KGE(grid_all, obs), -->
<!--             statn2011 = KGE(statn_2011, obs), -->
<!--             statn2012 = KGE(statn_2012, obs), -->
<!--             statn2013 = KGE(statn_2013, obs), -->
<!--             statn2014 = KGE(statn_2014, obs), -->
<!--             statn2015 = KGE(statn_2015, obs), -->
<!--             statn2016 = KGE(statn_2016, obs), -->
<!--             statn2017 = KGE(statn_2017, obs), -->
<!--             statn2018 = KGE(statn_2018, obs), -->
<!--             statn2019 = KGE(statn_2019, obs), -->
<!--             statn2020 = KGE(statn_2020, obs), -->
<!--             statnall = KGE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 2) -->

<!-- flow_kge <- flow_year %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
<!--   pivot_wider(names_from = 'year', values_from = 'kge') -->

<!-- flow_kge %>% -->
<!--   kable(.) %>% -->
<!--   kable_styling() -->

<!-- flow_plot <- flow_year %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
<!--   mutate(year = as.factor(year)) -->

<!-- kge_plot_cy <- ggplot(flow_plot, aes(year, kge, color = model_run)) +  -->
<!--   geom_point(size = 3) + -->
<!--   scale_color_manual(name="model_run", values=c("grid2011"="seagreen",  -->
<!--                                             "grid2012"="seagreen2",  -->
<!--                                             "grid2013"="steelblue", -->
<!--                                             "grid2014"='dodgerblue',  -->
<!--                                             "grid2015" = "cyan3", -->
<!--                                             'grid2016' = 'blue', -->
<!--                                             'grid2017' = 'blue4', -->
<!--                                             'grid2018' = 'cadetblue', -->
<!--                                             'grid2019' = 'lightgreen', -->
<!--                                             'grid2020' = 'olivedrab', -->
<!--                                             'gridall' = 'steelblue3', -->
<!--                                             "statn2011"="maroon",  -->
<!--                                             "statn2012"="deeppink4",  -->
<!--                                             "statn2013"="deeppink", -->
<!--                                             "statn2014"='purple',  -->
<!--                                             "statn2015" = "mediumorchid1", -->
<!--                                             'statn2016' = 'indianred', -->
<!--                                             'statn2017' = 'sienna', -->
<!--                                             'statn2018' = 'salmon2', -->
<!--                                             'statn2019' = 'mediumpurple1', -->
<!--                                             'statn2020' = 'violetred', -->
<!--                                             'statnall' = 'red')) + -->
<!--   theme_bw() -->

<!-- ggplotly(kge_plot_cy) -->

<!-- ``` -->

<!-- ### Annual KGE plots -->

<!-- ```{r wy plots, echo = F} -->

<!-- plot_kge <- function(calyear) { -->
<!--   flow_plot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = model_run, -->
<!--                y = kge)) + -->
<!--     geom_col() + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
<!-- } -->

<!-- name <- levels(flow_plot$year) -->

<!-- lapply(name, plot_kge) -->

<!-- ``` -->

<!-- # Ensembles -->

<!-- ## Hydrograph -->

<!-- ```{r boulder cr gage, echo = F} -->

<!-- #pull in Boulder Creek @ N 75th gage -->

<!-- bouldcr <- readNWISdv(siteNumbers = "06730200", -->
<!--                           parameterCd = "00060",  -->
<!--                           startDate = "2011-01-01",  -->
<!--                           endDate = "2020-12-31")  %>% -->
<!--   dplyr::select(date = Date, -->
<!--          q_cfs = X_00060_00003) %>% -->
<!--   mutate(bouldcr = q_cfs/35.3146662) %>% -->
<!--   dplyr::select(-q_cfs) %>% -->
<!--   mutate(year = year(date)) -->

<!-- ``` -->

<!-- ```{r ensemble hydrographs, echo = F} -->

<!-- ensem <- flow %>% -->
<!--   rowwise() %>% -->
<!--   mutate(grid_ensemble = mean(c(grid_2011, grid_2012, -->
<!--                                 grid_2013, grid_2014, -->
<!--                                 grid_2015, grid_2016, -->
<!--                                 grid_2017, grid_2018, -->
<!--                                 grid_2019, grid_2020)), -->
<!--          statn_ensemble = mean(c(statn_2011, statn_2012, -->
<!--                                  statn_2013, statn_2014, -->
<!--                                  statn_2015, statn_2016, -->
<!--                                  statn_2017, statn_2018, -->
<!--                                  statn_2019, statn_2020)), -->
<!--          all_ensemble = mean(c(grid_2011, grid_2012, -->
<!--                                grid_2013, grid_2014, -->
<!--                                grid_2015, grid_2016, -->
<!--                                grid_2017, grid_2018, -->
<!--                                grid_2019, grid_2020, -->
<!--                                statn_2011, statn_2012, -->
<!--                                statn_2013, statn_2014, -->
<!--                                statn_2015, statn_2016, -->
<!--                                statn_2017, statn_2018, -->
<!--                                statn_2019, statn_2020, -->
<!--                                grid_all, statn_all))) %>% -->
<!--   dplyr::select(date, grid_ensemble, statn_ensemble,  -->
<!--          all_ensemble, grid_all,  -->
<!--          statn_all, obs)  -->

<!-- ensem_pivot <- ensem %>% -->
<!--   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>% -->
<!--   mutate(year = as.factor(year(date))) -->

<!-- q_ensemble <- ggplot(ensem_pivot, aes(date, q_m3s, color = cal_run)) + -->
<!--   geom_line() + -->
<!--   scale_color_manual(name="cal_run", values=c('obs'='black', -->
<!--                                             "grid_ensemble"="maroon",  -->
<!--                                             "statn_ensemble"="darkturquoise",  -->
<!--                                             "grid_all"="purple1", -->
<!--                                             "statn_all"='springgreen4',  -->
<!--                                             "all_ensemble" = "orange")) + -->
<!--   geom_line(data = bouldcr, aes(date, bouldcr/10), color = 'darkgrey') + -->
<!--   scale_y_continuous(name = 'Q_m3s', -->
<!--                     sec.axis = sec_axis(~.*10, name='BoulderCr_cms')) + -->
<!--   theme_bw() -->

<!-- ggplotly(q_ensemble) %>% -->
<!--   add_lines(data=bouldcr, x=~date, y=~bouldcr, colors=NULL, yaxis="y2",  -->
<!--               inherit=FALSE, showlegend = FALSE) %>% -->
<!--   layout(yaxis2 = list(overlaying = "y", side = "right", -->
<!--                        color = 'darkgray', -->
<!--                        title = "BoulderCr_cms"), -->
<!--          legend = list(x = 1.1, y = 0.95)) -->

<!-- ``` -->

<!-- ## Annual hydrographs -->

<!-- ```{r hydrogs by cy, echo = F} -->

<!-- plotqensem_cy <- function(calyear) { -->
<!--   {ensem_pivot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = date, -->
<!--                y = q_m3s, -->
<!--                color = cal_run)) + -->
<!--     geom_line() + -->
<!--     scale_color_manual(name="cal_run", values=c('obs' = 'black', -->
<!--                                             "grid_ensemble"="maroon",  -->
<!--                                             "statn_ensemble"="darkturquoise",  -->
<!--                                             "grid_all"="purple1", -->
<!--                                             "statn_all"='springgreen4',  -->
<!--                                             "all_ensemble" = "orange")) + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() -->
<!--     } %>% -->
<!--     ggplotly() -->
<!-- } -->

<!-- name <- levels(ensem_pivot$year) -->

<!-- try <- lapply(name, plotqensem_cy) -->

<!-- htmltools::tagList(try) -->

<!-- try -->

<!-- ``` -->

<!-- ## KGE -->

<!-- ### KGE for ensembles (entire period) -->

<!-- ```{r ensemble kge, echo = F} -->

<!-- ensem_kge_all <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
<!--             all_ensemble = KGE(all_ensemble, obs), -->
<!--             grid_all = KGE(grid_all, obs), -->
<!--             statn_all = KGE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 2) -->

<!-- kable(ensem_kge_all) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- ``` -->

<!-- ### Annual KGEs for ensembles -->

<!-- ```{r annual kge ensemble, echo = F} -->

<!-- yr_kge_ensem <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   mutate(year = year(date)) %>% -->
<!--   group_by(year) %>% -->
<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
<!--             all_ensemble = KGE(all_ensemble, obs), -->
<!--             grid_all = KGE(grid_all, obs), -->
<!--             statn_all = KGE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 2) -->

<!-- yr_kge_table <- yr_kge_ensem %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
<!--   pivot_wider(names_from = 'year', values_from = 'kge') -->

>>>>

library(tidyverse)
library(plotly)
library(lubridate)
library(knitr)
library(kableExtra)
library(dataRetrieval)
library(hydroGOF)
library(sp)
library(raster)
library(sf)
library(mapview)
library(here)
library(scales)
library(dataRetrieval)
library(tmap)
library(ggpubr)
library(gridExtra)
library(stringr)

@@

## Burn parameters

@@

burn_params <- bind_rows(grid_burn, statn_burn) %>%
  ungroup() %>%
  mutate(across(c(luca_a_rain:luca_soilDistMPSLPS), as.numeric)) %>%
  group_by(cal) %>%
  mutate(across(c(luca_a_rain:luca_soilDistMPSLPS), mean)) %>%
  filter(soilID == 22) %>%
  dplyr::select(-soilID) %>% 
  pivot_longer(!c(cal, input_data, year_missing), 
               names_to = 'params',
               values_to = 'value') %>% 
  mutate(params = str_remove(params, 'luca_')) %>%
  mutate(params = as.factor(params),
         burn = 'yes')

@@

plot_burnparams <- function(param_name) {
  burn_params %>%
    filter(params == param_name) %>%
    ggplot(aes(y = value,
               x = year_missing,
               color = input_data)) +
    geom_point(size = 3) +
    ggtitle(param_name) +
    theme_bw()
}

name <- levels(burn_params$params)

lapply(name, plot_burnparams)

@@

## Combined parameters

The two burned HRU parameters were averaged together.

```{r}
params <- params %>%
  mutate(burn = 'no')

params_combo <- bind_rows(params,
                          burn_params %>%
                            rename(param = params))

#function to plot all params
plot_params <- function(param_name) {
  params_combo %>%
    filter(param == param_name) %>%
    ggplot(aes(x = year_missing,
               y = value,
               shape = burn, 
               color = input_data)) + 
    geom_point(size = 3) + 
    ggtitle(param_name) +
    theme_bw()
}

name <- levels(params_combo$param)

# Outlet results

## Hydrograph

```{r hydrographs, echo = F}
flow <- read_csv('discharge_all.csv') %>%
  replace(.==-9999, NA)

flow_pivot <- flow %>%
  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
  mutate(year = as.factor(year(date)))

q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line() +
  scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            "grid_2011"="seagreen",
                                            "grid_2012"="seagreen2",
                                            "grid_2013"="steelblue",
                                            "grid_2014"='dodgerblue',
                                            "grid_2015" = "cyan3",
                                            'grid_2016' = 'blue',
                                            'grid_2017' = 'blue4',
                                            'grid_2018' = 'cadetblue',
                                            'grid_2019' = 'lightgreen',
                                            'grid_2020' = 'olivedrab',
                                            'grid_all' = 'steelblue3',
                                            "statn_2011"="maroon",
                                            "statn_2012"="deeppink4",
                                            "statn_2013"="deeppink",
                                            "statn_2014"='purple',
                                            "statn_2015" = "mediumorchid1",
                                            'statn_2016' = 'indianred',
                                            'statn_2017' = 'sienna',
                                            'statn_2018' = 'salmon2',
                                            'statn_2019' = 'mediumpurple1',
                                            'statn_2020' = 'violetred',
                                            'statn_all' = 'red'))

ggplotly(q)

## KGE

### Overall KGE

```{r kge overall, echo = F}

flow_kge_all <- flow %>%
  summarize(grid2011 = KGE(grid_2011, obs),
            grid2012 = KGE(grid_2012, obs),
            grid2013 = KGE(grid_2013, obs),
            grid2014 = KGE(grid_2014, obs),
            grid2015 = KGE(grid_2015, obs),
            grid2016 = KGE(grid_2016, obs),
            grid2017 = KGE(grid_2017, obs),
            grid2018 = KGE(grid_2018, obs),
            grid2019 = KGE(grid_2019, obs),
            grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs),
            statn2011 = KGE(statn_2011, obs),
            statn2012 = KGE(statn_2012, obs),
            statn2013 = KGE(statn_2013, obs),
            statn2014 = KGE(statn_2014, obs),
            statn2015 = KGE(statn_2015, obs),
            statn2016 = KGE(statn_2016, obs),
            statn2017 = KGE(statn_2017, obs),
            statn2018 = KGE(statn_2018, obs),
            statn2019 = KGE(statn_2019, obs),
            statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_kge_all <- flow_kge_all %>%
  pivot_longer(everything()) %>%
  arrange(value)

kable(flow_kge_all) %>%
  kable_styling(full_width = F)

### KGE by year

```{r kge by year, echo = F}

flow_year <- flow %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(grid2011 = KGE(grid_2011, obs),
            grid2012 = KGE(grid_2012, obs),
            grid2013 = KGE(grid_2013, obs),
            grid2014 = KGE(grid_2014, obs),
            grid2015 = KGE(grid_2015, obs),
            grid2016 = KGE(grid_2016, obs),
            grid2017 = KGE(grid_2017, obs),
            grid2018 = KGE(grid_2018, obs),
            grid2019 = KGE(grid_2019, obs),
            grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs),
            statn2011 = KGE(statn_2011, obs),
            statn2012 = KGE(statn_2012, obs),
            statn2013 = KGE(statn_2013, obs),
            statn2014 = KGE(statn_2014, obs),
            statn2015 = KGE(statn_2015, obs),
            statn2016 = KGE(statn_2016, obs),
            statn2017 = KGE(statn_2017, obs),
            statn2018 = KGE(statn_2018, obs),
            statn2019 = KGE(statn_2019, obs),
            statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_kge <- flow_year %>%
  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
  pivot_wider(names_from = 'year', values_from = 'kge')

flow_kge %>%
  kable(.) %>%
  kable_styling()

flow_plot <- flow_year %>%
  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
  mutate(year = as.factor(year))

kge_plot_cy <- ggplot(flow_plot, aes(year, kge, color = model_run)) +
  geom_point(size = 3) +
  scale_color_manual(name="model_run", values=c("grid2011"="seagreen",
                                            "grid2012"="seagreen2",
                                            "grid2013"="steelblue",
                                            "grid2014"='dodgerblue',
                                            "grid2015" = "cyan3",
                                            'grid2016' = 'blue',
                                            'grid2017' = 'blue4',
                                            'grid2018' = 'cadetblue',
                                            'grid2019' = 'lightgreen',
                                            'grid2020' = 'olivedrab',
                                            'gridall' = 'steelblue3',
                                            "statn2011"="maroon",
                                            "statn2012"="deeppink4",
                                            "statn2013"="deeppink",
                                            "statn2014"='purple',
                                            "statn2015" = "mediumorchid1",
                                            'statn2016' = 'indianred',
                                            'statn2017' = 'sienna',
                                            'statn2018' = 'salmon2',
                                            'statn2019' = 'mediumpurple1',
                                            'statn2020' = 'violetred',
                                            'statnall' = 'red')) +
  theme_bw()

ggplotly(kge_plot_cy)

### Annual KGE plots

```{r wy plots, echo = F}

plot_kge <- function(calyear) {
  flow_plot %>%
    filter(year == calyear) %>%
    ggplot(aes(x = model_run,
               y = kge)) +
    geom_col() +
    ggtitle(calyear) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust=1))
}

name <- levels(flow_plot$year)

lapply(name, plot_kge)

# Ensembles

## Hydrograph

```{r ensemble hydrographs, echo = F}

ensem <- flow %>%
  rowwise() %>%
  mutate(grid_ensemble = mean(c(grid_2011, grid_2012,
                                grid_2013, grid_2014,
                                grid_2015, grid_2016,
                                grid_2017, grid_2018,
                                grid_2019, grid_2020)),
         statn_ensemble = mean(c(statn_2011, statn_2012,
                                 statn_2013, statn_2014,
                                 statn_2015, statn_2016,
                                 statn_2017, statn_2018,
                                 statn_2019, statn_2020)),
         all_ensemble = mean(c(grid_2011, grid_2012,
                               grid_2013, grid_2014,
                               grid_2015, grid_2016,
                               grid_2017, grid_2018,
                               grid_2019, grid_2020,
                               statn_2011, statn_2012,
                               statn_2013, statn_2014,
                               statn_2015, statn_2016,
                               statn_2017, statn_2018,
                               statn_2019, statn_2020,
                               grid_all, statn_all))) %>%
  dplyr::select(date, grid_ensemble, statn_ensemble,
         all_ensemble, grid_all,
         statn_all, obs)

ensem_pivot <- ensem %>%
  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
  mutate(year = as.factor(year(date)))

q_ensemble <- ggplot(ensem_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line() +
  scale_color_manual(name="cal_run", values=c('obs'='black',
                                            "grid_ensemble"="maroon",
                                            "statn_ensemble"="darkturquoise",
                                            "grid_all"="purple1",
                                            "statn_all"='springgreen4',
                                            "all_ensemble" = "orange")) +
  geom_line(data = bouldcr, aes(date, bouldcr/10), color = 'darkgrey') +
  scale_y_continuous(name = 'Q_m3s',
                    sec.axis = sec_axis(~.*10, name='BoulderCr_cms')) +
  theme_bw()

ggplotly(q_ensemble) %>%
  add_lines(data=bouldcr, x=~date, y=~bouldcr, colors=NULL, yaxis="y2",
              inherit=FALSE, showlegend = FALSE) %>%
  layout(yaxis2 = list(overlaying = "y", side = "right",
                       color = 'darkgray',
                       title = "BoulderCr_cms"),
         legend = list(x = 1.1, y = 0.95))

## KGE

### KGE for ensembles (entire period)

```{r ensemble kge, echo = F}

ensem_kge_all <- ensem %>%
  ungroup() %>%
  summarize(grid_ensemble = KGE(grid_ensemble, obs),
            statn_ensemble = KGE(statn_ensemble, obs),
            all_ensemble = KGE(all_ensemble, obs),
            grid_all = KGE(grid_all, obs),
            statn_all = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

kable(ensem_kge_all) %>%
  kable_styling(full_width = F)

### Annual KGEs for ensembles

```{r annual kge ensemble, echo = F}

yr_kge_ensem <- ensem %>%
  ungroup() %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(grid_ensemble = KGE(grid_ensemble, obs),
            statn_ensemble = KGE(statn_ensemble, obs),
            all_ensemble = KGE(all_ensemble, obs),
            grid_all = KGE(grid_all, obs),
            statn_all = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

yr_kge_table <- yr_kge_ensem %>%
  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
  pivot_wider(names_from = 'year', values_from = 'kge')

yr_kge_table %>%
  kable(.) %>%
  kable_styling()

yr_kge_plot <- yr_kge_ensem %>%
  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
  mutate(year = as.factor(year))

#plot annual kge vals for ensembles
plot_kge_yr_ensem <- function(calyear) {
  yr_kge_plot %>%
    filter(year == calyear) %>%
    ggplot(aes(x = model_run,
               y = kge)) +
    geom_col() +
    ggtitle(calyear) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust=1))
}

name <- levels(yr_kge_plot$year)

lapply(name, plot_kge_yr_ensem)

### Monthly KGEs for ensembles

```{r monthly kge ensemble, echo = F}

mo_kge <- ensem %>%
  ungroup() %>%
  drop_na() %>%
  mutate(month = month(date)) %>%
  group_by(month) %>%
  summarize(grid_ensemble = KGE(grid_ensemble, obs),
            statn_ensemble = KGE(statn_ensemble, obs),
            all_ensemble = KGE(all_ensemble, obs),
            grid_all = KGE(grid_all, obs),
            statn_all = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

kable(mo_kge) %>%
  kable_styling(full_width = F)

mo_pivot <- mo_kge %>%
  pivot_longer(!month, names_to = 'cal_run', values_to = 'KGE') %>%
  drop_na()

kge_plot_mo <- ggplot(mo_pivot, aes(month, KGE, color = cal_run)) + geom_point(size = 3) +
    scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon",
                                            "statn_ensemble"="darkturquoise",
                                            "grid_all"="purple1",
                                            "statn_all"='springgreen4',
                                            "all_ensemble" = "orange")) +
  theme_bw()

ggplotly(kge_plot_mo)

## RMSE

### Ensemble RMSE for entire period

```{r ensemble rmse, echo = F}

ensem_rmse_all <- ensem %>%
  ungroup() %>%
  summarize(grid_ensemble = rmse(grid_ensemble, obs),
            statn_ensemble = rmse(statn_ensemble, obs),
            all_ensemble = rmse(all_ensemble, obs),
            grid_all = rmse(grid_all, obs),
            statn_all = rmse(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 4)

kable(ensem_rmse_all) %>%
  kable_styling(full_width = F)

### Annual RMSE for ensembles

```{r annual rmse ensem, echo = F}

yr_rmse_ensem <- ensem %>%
  ungroup() %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(grid_ensemble = rmse(grid_ensemble, obs),
            statn_ensemble = rmse(statn_ensemble, obs),
            all_ensemble = rmse(all_ensemble, obs),
            grid_all = rmse(grid_all, obs),
            statn_all = rmse(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 4)

yr_rmse_table <- yr_rmse_ensem %>%
  pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>%
  pivot_wider(names_from = 'year', values_from = 'rmse')

yr_rmse_table %>%
  kable(.) %>%
  kable_styling()

yr_rmse_plot <- yr_rmse_ensem %>%
  pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>%
  mutate(year = as.factor(year))

#plot annual rmse vals for ensembles
plot_rmse_yr_ensem <- function(calyear) {
  yr_rmse_plot %>%
    filter(year == calyear) %>%
    ggplot(aes(x = model_run,
               y = rmse)) +
    geom_col() +
    ggtitle(calyear) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust=1))
}

name <- levels(yr_rmse_plot$year)

lapply(name, plot_rmse_yr_ensem)

### Monthly RMSEs for ensembles

```{r month ensem rmse, echo = F}

mo_rmse <- ensem %>%
  ungroup() %>%
  drop_na() %>%
  mutate(month = month(date)) %>%
  group_by(month) %>%
  summarize(grid_ensemble = rmse(grid_ensemble, obs),
            statn_ensemble = rmse(statn_ensemble, obs),
            all_ensemble = rmse(all_ensemble, obs),
            grid_all = rmse(grid_all, obs),
            statn_all = rmse(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 4)

kable(mo_rmse) %>%
  kable_styling(full_width = F)

mo_pivot2 <- mo_rmse %>%
  pivot_longer(!month, names_to = 'cal_run', values_to = 'RMSE') %>%
  drop_na()

rmse_plot_mo <- ggplot(mo_pivot2, aes(month, RMSE, color = cal_run)) + geom_point(size = 3) +
    scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon",
                                            "statn_ensemble"="darkturquoise",
                                            "grid_all"="purple1",
                                            "statn_all"='springgreen4',
                                            "all_ensemble" = "orange")) +
  theme_bw()

ggplotly(rmse_plot_mo)

## NSE

### Ensemble NSE for entire period

```{r nse all, echo = F}

ensem_nse_all <- ensem %>%
  ungroup() %>%
  summarize(grid_ensemble = NSE(grid_ensemble, obs),
            statn_ensemble = NSE(statn_ensemble, obs),
            all_ensemble = NSE(all_ensemble, obs),
            grid_all = NSE(grid_all, obs),
            statn_all = NSE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

kable(ensem_nse_all) %>%
  kable_styling(full_width = F)

### Annual NSE for ensembles

```{r annual nse, echo = F}

yr_nse_ensem <- ensem %>%
  ungroup() %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(grid_ensemble = NSE(grid_ensemble, obs),
            statn_ensemble = NSE(statn_ensemble, obs),
            all_ensemble = NSE(all_ensemble, obs),
            grid_all = NSE(grid_all, obs),
            statn_all = NSE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 4)

yr_nse_table <- yr_nse_ensem %>%
  pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>%
  pivot_wider(names_from = 'year', values_from = 'nse')
